### 2014-05-21 intro.tex
New para in intro

\textcolor{white}{.}\hspace{\parindent} A Remy-generated algorithm, or
RemyCC, measures the \textbf{rate} of acknowledgment arrivals, and the
\textbf{rate} of transmission implied by the echoed sender timestamps
in those acknowledgments. We can quantify the value of these signals
by removing one of them and rerunning the optimization process. The
results are markedly worse with either signal removed.  From
Figure~\ref{f:tpdelaydb4}:
%}

@@

>>>>

\textcolor{white}{.}\hspace{\parindent} A Remy-generated algorithm, or
RemyCC, measures the \textbf{rate} of acknowledgment arrivals, and the
\textbf{rate} of transmission implied by the echoed sender timestamps
in those acknowledgments. We can quantify the value of these signals
by removing one of them and rerunning the optimization process. The
results are markedly worse with either signal removed.  From
Figure~\ref{f:tpdelaydb4} (a 15~Mbps link with 8 contending nodes):
%}

@@

More broadly, automated protocol-design tools lead to a style of
design where the value of information can be evaluated empirically. We
may give Remy access to a new congestion signal---either derivable
from existing TCP acknowledgments from the receiver, or based on new
information from the network---and measure how much the resulting
congestion-control algorithm improves over the status quo. Similarly,
we can knock out an existing signal and rerun Remy to measure how much
the loss hurts the resulting algorithm's performance.

After investigating many candidate signals, this design process led us
to computer-generated algorithms that collect four congestion signals
(Section~\ref{ss:signals}). \textbf{None of these signals} is
collected by existing TCP congestion-control algorithms, but our
simulation experiments indicate they are each individually valuable on
top of the other three.

\subsection{Windowing and pacing work well together}

### 2014-05-21 remy_design.tex
New para in intro

\subsection{Compactly representing the sender's state}

In principle, for any given network, there is an {\em optimal}
congestion-control scheme that maximizes the expected total of the
endpoints' objective functions. Such an algorithm would relate (1) the
entire history of observations seen thus far (e.g.~the
contents and timing of every ACK) and (2) the entire history of
packets already sent, to the best action at any given moment between sending a new packet or abstaining. However, the search for such an algorithm is likely
intractable; on a general Dec-POMDP it is
NEXP-complete~\cite{Bernstein2002}.

>>>>

\subsection{Compactly representing the sender's state}
\label{ss:signals}
In principle, for any given network, there is an {\em optimal}
congestion-control scheme that maximizes the expected total of the
endpoints' objective functions. Such an algorithm would relate (1) the
entire history of observations seen thus far (e.g.~the
contents and timing of every ACK) and (2) the entire history of
packets already sent, to the best action at any given moment between sending a new packet or abstaining. However, the search for such an algorithm is likely
intractable; on a general Dec-POMDP it is
NEXP-complete~\cite{Bernstein2002}.
